---
title: "Global Plastic Waste"
output: 
  html_document
---

```{r setup, include=FALSE}
#https://github.com/LaineyJ/TidyTuesdays/blob/master/2019-05-21/Global%20Plastic%20Waste.R
#install.packages("flexdashboard")
#install.packages("janitor")
#install.packages("extrafont")
#install.packages("gridExtra")
#install.packages("dplyr")
#install.packages("tidyverse")
#install.packages("ggplot2")
#install.packages("gifski")
#install.packages("png")
#install.packages("transformr")
#install.packages("plotly")
#install.packages("flexdashboard")
#install.packages("RColorBrewer")
#install.packages("ggforce")
#install.packages("gganimate")
library(janitor)
library(extrafont)
library(gridExtra)
library(tidyverse)
library(gifski)
library(png)
library(transformr)
library(ggplot2)
library(gganimate)
library(flexdashboard)
library(ggforce)
library(RColorBrewer)
library(gridExtra)
library(plotly)
library(dplyr)
```
```{r linechart}
wasteinyears<-readr::read_csv("./Data/global-plastics-production.csv")
#glimpse(wasteinyears)
PlasticProductionInallYears<-wasteinyears %>%
ggplot(aes(x=Year,y=`Global plastics production (million tonnes) (tonnes)`))+
  geom_line(color='red')+
  ggtitle("Plastic Production in Million Tonnes")+
  labs(x = "Year", y = "Global Plastic Production (million tonnes)")+
  theme_classic()
```
```{r}
### Plastic Produced in all years
library(plotly)
ggplotly(PlasticProductionInallYears)
```
#install.packages("gifski")
#install.packages("png)
#install.packages("transformr")
#library(gifski)
#library(png)
#library(transformr)
#library(ggplot2)
#library(gganimate)

Animation of Plastic Production in all years:

```{r animation}
theme_set(theme_bw())

#glimpse(wasteinyears)
PlasticProductionInallYears<-wasteinyears %>%
ggplot(aes(x=Year,y=`Global plastics production (million tonnes) (tonnes)`,group))+
  geom_line(color='red')+ggtitle("Plastic Production in Million Tonnes across all Years") 
  PlasticProductionInallYears +
    geom_point() +
    transition_reveal(Year) 
 #PlasticProductionInallYears + transition_time(Year) +
  #labs(title = "Year: {frame_time}") +
    # ease_aes("linear")
```
```{r boxplot}
### Plastic waste generation in 2010
plasticwaste_2010<-readr::read_csv("./Data/plastic-waste-generation-total.csv")
#glimpse(plasticwaste_2010)
Plasticwastegeneration2010<-plasticwaste_2010%>%
  filter(Entity %in% c("United States","Germany","Egypt","China","India"))%>%
  ggplot(aes(x=reorder(Entity,-`Plastic waste generation (tonnes, total) (tonnes per year)`),y=`Plastic waste generation (tonnes, total) (tonnes per year)`,fill=`Plastic waste generation (tonnes, total) (tonnes per year)`))+
  geom_bar(position="dodge",stat = "identity")+coord_flip()+ggtitle("Plastic Waste Generation (2010)") +
   scale_fill_distiller(palette = "Reds", direction = 1) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
   # panel.grid.major.y = element_line(color = "white"),
    panel.ontop = TRUE
  ) +
  labs(x = "Country", y = "Plastic Waste Generated (Tonnes)")
  

library(plotly)
ggplotly(Plasticwastegeneration2010)
```
```{r chloropleth}
###chloropleth map of Plastic production in 2010 across different countries.
#install.packages("plotly")
library(plotly)
# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)
# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)
plot_geo(plasticwaste_2010) %>%
  add_trace(
    z=~`Plastic waste generation (tonnes, total) (tonnes per year)`, color = ~`Plastic waste generation (tonnes, total) (tonnes per year)` , colors = 'Reds',
     locations = ~Code, marker = list(line = l)
  ) %>%
  colorbar(title = 'Plastic waste in Million Tonnes', ticksuffix = '') %>%
  layout(
    title = 'Plastic waste produced in 2010',
    geo = g
  )

```

```{r animations}
#Animation of Box plot for the Plastic waste generated in 2010
plasticwaste_2010<-readr::read_csv("./Data/plastic-waste-generation-total.csv")
#glimpse(plasticwaste_2010)
Plasticwastegeneration2010<-plasticwaste_2010%>%
  filter(Entity %in% c("United States","Germany","Egypt","China","India"))%>%
  ggplot(aes(x=reorder(Entity,-`Plastic waste generation (tonnes, total) (tonnes per year)`),y=`Plastic waste generation (tonnes, total) (tonnes per year)`,fill=`Plastic waste generation (tonnes, total) (tonnes per year)`))+
  geom_bar(position="dodge",stat = "identity")+coord_flip()+ggtitle("Plastic waste generation, 2010") +
   scale_fill_distiller(palette = "Reds", direction = 1) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
   # panel.grid.major.y = element_line(color = "white"),
    panel.ontop = TRUE
  ) +
  labs(x = "Country", y = "Plastic waste generated in Tonnes")
  
Plasticwastegeneration2010 + transition_states(`Plastic waste generation (tonnes, total) (tonnes per year)`, wrap = FALSE) +
  shadow_mark()

```
Plastic waste generated per person per day in Kg's

```{r barplot}

plasticfate<-readr::read_csv("./Data/global-plastic-fate.csv")
plasticfate
#glimpse(plasticfate)

plasticwaste_2015<-readr::read_csv("./Data/plastic-waste-by-sector.csv")
#plasticwaste_2015

plasticpercapita<-readr::read_csv("./Data/plastic-waste-per-capita.csv")
#plasticpercapita
#glimpse(plasticpercapita)
Plasticwastegenerationperperson2010<-plasticpercapita%>%
  filter(Entity %in% c("United States","United Kingdom","Brazil","China","Canada"
                       ,"Benin","India"))%>%
ggplot(aes(x=reorder(Entity,-`Per capita plastic waste (kilograms per person per day)`),y=`Per capita plastic waste (kilograms per person per day)`,fill=`Per capita plastic waste (kilograms per person per day)`))+
  geom_bar(position="dodge",stat = "identity")+coord_flip()+ggtitle("Plastic waste generation per person, 2010") +
scale_fill_distiller(palette = "Reds", direction = 1) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
   # panel.grid.major.y = element_line(color = "white"),
    panel.ontop = TRUE
  ) +
  labs(x = "plastic_waste_per_person_per_day", y = "Country")

Plasticwastegenerationperperson2010


library(plotly)
ggplotly(Plasticwastegenerationperperson2010)
```
Animation of Plastic waste generated per person per day in Kg's

```{r}

plasticfate<-readr::read_csv("./Data/global-plastic-fate.csv")
plasticfate
#glimpse(plasticfate)

plasticwaste_2015<-readr::read_csv("./Data/plastic-waste-by-sector.csv")
#plasticwaste_2015

plasticpercapita<-readr::read_csv("./Data/plastic-waste-per-capita.csv")
#plasticpercapita
#glimpse(plasticpercapita)
Plasticwastegenerationperperson2010<-plasticpercapita%>%
  filter(Entity %in% c("United States","United Kingdom","Brazil","China","Canada"
                       ,"Benin","India"))%>%
ggplot(aes(x=reorder(Entity,-`Per capita plastic waste (kilograms per person per day)`),y=`Per capita plastic waste (kilograms per person per day)`,fill=`Per capita plastic waste (kilograms per person per day)`))+
  geom_bar(position="dodge",stat = "identity")+coord_flip()+ggtitle("Plastic waste generation per person, 2010") +
scale_fill_distiller(palette = "Reds", direction = 1) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
   # panel.grid.major.y = element_line(color = "white"),
    panel.ontop = TRUE
  ) +
  labs(x = "plastic_waste_per_person_per_day", y = "Country")

Plasticwastegenerationperperson2010 + transition_states(Entity, wrap = FALSE) +
  shadow_mark()

```
Chloropleth map of plastic waste generated per person per day in kg
```{r}

#install.packages("plotly")
library(plotly)
# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)
# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)
plot_geo(plasticpercapita) %>%
  add_trace(
    z=~`Per capita plastic waste (kilograms per person per day)`, color = ~`Per capita plastic waste (kilograms per person per day)` , colors = 'Blues',
     locations = ~Code, marker = list(line = l)
  ) %>%
  colorbar(title = 'Plastic waste in Million Tonnes', ticksuffix = 'kg') %>%
  layout(
    title = 'Plastic Waste that is Generated per person per day in 2010',
    geo = g
  )



```
chloropleth map of mismanaged plastic waste across different countries
```{r}

inadequateplastic<-readr::read_csv("./Data/inadequately-managed-plastic.csv")
inadequateplastic


#install.packages("plotly")
library(plotly)
# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)
# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)
plot_geo(inadequateplastic) %>%
  add_trace(
    z=~`Share of plastic inadequately managed (%)`, color = ~`Share of plastic inadequately managed (%)` , colors = 'Blues',
     locations = ~Code, marker = list(line = l)
  ) %>%
  colorbar(title = 'Plastic waste in Million Tonnes', ticksuffix = '%') %>%
  layout(
    title = 'Share of plastic waste that is inadequately managed, 2010',
    geo = g
  )



```
```{r}

# Read in the data
coast_vs_waste <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-21/coastal-population-vs-mismanaged-plastic.csv")
mismanaged_vs_gdp <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-21/per-capita-mismanaged-plastic-waste-vs-gdp-per-capita.csv")
waste_vs_gdp <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-21/per-capita-plastic-waste-vs-gdp-per-capita.csv")
continent <- readr::read_csv("https://datahub.io/JohnSnowLabs/country-and-continent-codes-list/r/country-and-continent-codes-list-csv.csv")
```

```{r}
# Clean up names
coast_vs_waste <- clean_names(coast_vs_waste)
mismanaged_vs_gdp <- mismanaged_vs_gdp %>%
  set_names(c("entity", "code", "year", "mismg_kg_pp_pd", "gdp_per_capita", "total_population_gapminder"))
waste_vs_gdp <- waste_vs_gdp %>%
  set_names(c("entity", "code", "year", "waste_kg_pp_pd", "gdp_per_capita", "total_population_gapminder"))
continent <- clean_names(continent)
continent$continent_code <- ifelse(is.na(continent$continent_code), "NA", continent$continent_code)

# Merge dfs
waste_df <- merge(coast_vs_waste, mismanaged_vs_gdp, by = c("code", "year"))
waste_df <- merge(waste_df, waste_vs_gdp, by = c("code", "year"))
waste_df <- merge(waste_df, continent, by.x = "code", by.y = "three_letter_country_code")
waste_df <- select(waste_df, -c(country_name, two_letter_country_code, country_number))

# Exclude countries with no data
no_data <- waste_df %>%
  filter(is.na(mismanaged_plastic_waste_tonnes) & is.na(mismg_kg_pp_pd) & is.na(waste_kg_pp_pd) & year == 2010) %>%
  select(code, entity)

waste_df <- waste_df %>%
  filter(!code %in% no_data$code) %>%
  select(-c(entity.x, entity.y, total_population_gapminder.x, total_population_gapminder.y, gdp_per_capita.x)) %>%
  rename(gdp_per_capita = gdp_per_capita.y) %>%
  mutate(coastal_prop = coastal_population / total_population_gapminder)
waste_df$coastal_prop <- ifelse(waste_df$coastal_prop > 1, 1, waste_df$coastal_prop)

# Filter to only 2010 data
waste_2010 <- waste_df %>%
  filter(!is.na(waste_kg_pp_pd) & !is.na(mismanaged_plastic_waste_tonnes) & !is.na(mismg_kg_pp_pd) &
           !is.na(gdp_per_capita) & !is.na(total_population_gapminder & waste_kg_pp_pd < 1)) %>%
  select(-year)
```


```{r}
plt_l <- waste_2010 %>%
  ggplot(aes(x = coastal_population, y = mismanaged_plastic_waste_tonnes)) +
  geom_point(alpha = 0.75, aes(size = total_population_gapminder, color = continent_name)) +
  geom_smooth(method = "lm", se = FALSE, color = "grey20", size = 0.75, linetype = "dotted") +
  geom_smooth(data = filter(waste_2010, continent_name == "Oceania"), method = "lm",
              se = FALSE, color = "grey20", size = 0.75, linetype = "dashed")+
  scale_y_log10()+scale_x_log10()
plt_l
```




```{r}
plt_gdp <- waste_2010 %>%
  ggplot(aes(x = gdp_per_capita, y = mismg_kg_pp_pd)) +
  geom_point(alpha = 0.75, aes(size = total_population_gapminder, color = continent_name)) +
  # geom_smooth(method = "lm", se = FALSE, color = "grey20", size = 0.75, linetype = "dotted") +
  # geom_smooth(data = filter(waste_2010, continent_name == "Oceania"), method = "lm",
  #             se = FALSE, color = "grey20", size = 0.75, linetype = "dashed")+
  scale_x_log10()
plt_gdp
``` 


```{r}
# Chloropleth of gdp_per_capita vs mismanaged plastic waste in tonnes
#install.packages("plotly")
library(plotly)
# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)

 plot_geo(waste_2010) %>%
  add_trace(
    z = ~mismanaged_plastic_waste_tonnes , color = ~mismanaged_plastic_waste_tonnes , colors = 'Blues',
    text = ~continent_name, locations = ~code, marker = list(line = l)
  ) %>%
  colorbar(title = 'Mismanaged Plastic waste in Tonnes', tickprefix = '') %>%
  layout(
    title = '2010 Global Wastage',
    geo = g
  )

```

```{r}
# Proportion of coastal pop vs. mismgd plastic
# Graph setup
plt <- waste_2010 %>%
  ggplot(aes(x = coastal_prop, y = mismg_kg_pp_pd)) +
  geom_point(alpha = 0.75, aes(size = total_population_gapminder, color = continent_name)) +
  geom_smooth(method = "lm", se = FALSE, color = "grey20", size = 0.75, linetype = "dotted") +
  geom_smooth(data = filter(waste_2010, continent_name == "Oceania"), method = "lm",
              se = FALSE, color = "grey20", size = 0.75, linetype = "dashed")

# Style modifications
plt <- plt +
  labs(title = "AFFECT OF RESIDENT PROPORTION ON CONTINENT'S MISMANAGED WASTE PER CAPITA",
       caption = "Size of dot = total population",
       x = "Coastal Population / Total Population", y = "Mismanaged Waste per Person per Day (kg)") +
  theme(text = element_text(family = "Franklin Gothic Medium"),
        plot.title = element_text(family = "Franklin Gothic Heavy"),
        plot.subtitle = element_text(size = 10),
        plot.background = element_rect(fill = "whitesmoke"),
        panel.background = element_rect(fill = "whitesmoke"),
        legend.background = element_rect(fill = "whitesmoke"),
        panel.grid = element_line(color = "grey90")) +
  scale_size(guide = "none") +
  scale_color_brewer(name = "Continent", palette = "Dark2")

#plot(plt)
```

```{r}
#install.packages("plotly")
library(plotly)
ggplotly(plt)
```

```{r}
# Box plot of continent vs. mismanaged waste
oceania_med <- median(filter(waste_2010, continent_name == "Oceania")$mismg_kg_pp_pd)

# Graph setup
plt1 <- waste_2010 %>%
    ggplot(aes(x = reorder(continent_name, mismg_kg_pp_pd, FUN = median),y = mismg_kg_pp_pd)) +
  geom_boxplot(aes(fill = continent_name))
plt1
```
```{r}
# Style modifications
library(RColorBrewer)

plt1 <- plt1 +
  scale_fill_manual(values = brewer.pal(6, "Dark2"))+
  labs(title = "Continent vs Mismanaged Plastic Waste (PPPD)",
       caption = "",
       x = "Continent", y = "Mismanaged Waste per Person per Day (kg)") +
  theme(text = element_text(family = "Franklin Gothic Medium"),
        plot.title = element_text(family = "Franklin Gothic Heavy"),
        legend.position = "none",
        plot.background = element_rect(fill = "whitesmoke"),
        panel.background = element_rect(fill = "whitesmoke"),
        panel.grid = element_line(color = "grey90")) +
  scale_fill_brewer(palette = "Dark2") +
   theme_minimal()

# Adding annotation
plt1 <- plt1 +
  geom_hline(yintercept = oceania_med, linetype = "dashed")
#plot(plt1)
library(plotly)
ggplotly(plt1)
```
```{r}
#violin
plt1_violin <- waste_2010 %>%
  ggplot(aes(x = reorder(continent_name, mismg_kg_pp_pd, FUN = median),y = mismg_kg_pp_pd)) +
geom_violin(aes(fill = continent_name),trim=FALSE) +
    labs(title = "Continent vs Mismanaged Plastic Waste (PPPD)",
       caption = "",
       x = "Continent", y = "Mismanaged Waste per Person per Day (kg)") +
  theme(text = element_text(family = "Franklin Gothic Medium"),
        plot.title = element_text(family = "Franklin Gothic Heavy"),
        legend.position = "none",
        plot.background = element_rect(fill = "whitesmoke"),
        panel.background = element_rect(fill = "whitesmoke"),
        panel.grid = element_line(color = "grey90")) +
  scale_fill_brewer(palette = "Dark2")+
  theme_minimal()
plt1_violin
```

```{r}
### Strip Chart of continent vs. mismanaged waste
plt_strip <- waste_2010 %>%
    ggplot(aes(x = reorder(continent_name, mismg_kg_pp_pd, FUN = median),y = mismg_kg_pp_pd)) +
  geom_jitter(position=position_jitter(0.2), cex=1.2) +
  stat_summary(fun.y=mean, geom="point", shape=18,
                 size=3, color="red")+
  labs(title = "Continent vs Mismanaged Plastic Waste (PPPD)",
       caption = "",
       x = "Continent", y = "Mismanaged Waste per Person per Day (kg)") +
  theme(text = element_text(family = "Franklin Gothic Medium"),
        plot.title = element_text(family = "Franklin Gothic Heavy"),
        legend.position = "none",
        plot.background = element_rect(fill = "whitesmoke"),
        panel.background = element_rect(fill = "whitesmoke"),
        panel.grid = element_line(color = "grey90")) +
  scale_fill_brewer(palette = "Dark2")+
  theme_minimal()
plt_strip
```


```{r}
# Strip Chart with Violin
plt_strip_violin <- waste_2010 %>%
    ggplot(aes(x = reorder(continent_name, mismg_kg_pp_pd, FUN = median),y = mismg_kg_pp_pd)) +
  geom_violin(trim = FALSE)+
  geom_jitter(position=position_jitter(0.2), cex=1.2) +
  stat_summary(fun.y=mean, geom="point", shape=18,
                 size=3, color="red")+
  labs(title = "Continent vs Mismanaged Plastic Waste (PPPD)",
       caption = "",
       x = "Continent", y = "Mismanaged Waste per Person per Day (kg)") +
  theme(text = element_text(family = "Franklin Gothic Medium"),
        plot.title = element_text(family = "Franklin Gothic Heavy"),
        legend.position = "none",
        plot.background = element_rect(fill = "whitesmoke"),
        panel.background = element_rect(fill = "whitesmoke"),
        panel.grid = element_line(color = "grey90")) +
  scale_fill_brewer(palette = "Dark2")+
  theme_minimal()
  #theme_classic() 
plt_strip_violin
```
```{r}
#sina plot
#install.packages("ggforce")
library(tidyverse)
library(ggforce)
plt_sina <- waste_2010 %>%
  ggplot(aes(x = reorder(continent_name, mismg_kg_pp_pd, FUN = median),y = mismg_kg_pp_pd)) +
  geom_sina(aes(colour = continent_name), size = 1.5) +
  labs(title = "Continent vs Mismanaged Plastic Waste (PPPD)",
       x = "Continent", y = "Mismanaged Waste per Person per Day (kg)") +
  theme(text = element_text(family = "Franklin Gothic Medium"),
        plot.title = element_text(family = "Franklin Gothic Heavy"),
        legend.position = "none",
        plot.background = element_rect(fill = "whitesmoke"),
        panel.background = element_rect(fill = "whitesmoke"),
        panel.grid = element_line(color = "grey90"))+
  theme_minimal()
plt_sina
```

```{r}
### Box plot of continent vs. coastal proportion
# Box plot of continent vs. coastal proportion
oceania_prop_med <- median(filter(waste_2010, continent_name == "Oceania")$coastal_prop)

# Graph setup
plt2 <- waste_2010 %>%
  ggplot(aes(x = reorder(continent_name, coastal_prop, FUN = median),y = coastal_prop)) +
  geom_boxplot(aes(fill = continent_name))

# Style modifications
plt2 <- plt2 +
  labs(title = "Coastal Population Proportion",
       caption = "Source: https://ourworldindata.org/plastic-pollution",
       x = "Continent", y = "Coastal Population / Total Population") +
  theme(text = element_text(family = "Franklin Gothic Medium"),
        plot.title = element_text(family = "Franklin Gothic Heavy"),
        legend.position = "none",
        plot.background = element_rect(fill = "whitesmoke"),
        panel.background = element_rect(fill = "whitesmoke"),
        panel.grid = element_line(color = "grey90")) +
  scale_fill_brewer(palette = "Dark2")+
  theme_minimal()

# Adding annotation
plt2 <- plt2 +
  geom_hline(yintercept = oceania_prop_med, linetype = "dashed")

#plot_fin <- grid.arrange(plt, plt1, plt2, layout_matrix = rbind(c(1, 1), c(2, 3)))
#plot(plt2)
#ggsave("MismanagedWastePerCap_CoastalPopProp.jpeg", plt, width = 11.5, height = 8, units = "in", dpi = 320)
library(plotly)
ggplotly(plt2)
```
```{r}
### Strip Chart of continent vs coastal proportion
plt1_strip <- ggplot(waste_2010, aes(x = reorder(continent_name, coastal_prop, FUN = median),y = coastal_prop)) +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#999999")) +
  geom_violin(aes(fill = continent_name),trim=FALSE) +
  stat_summary(fun.y=mean, geom="point", shape=18,
                 size=3, color="red")+
   labs(title = "continent vs coastal proportion",
       caption = "",
       x = "Continent", y = "Coastal Proportion") +
  theme(text = element_text(family = "Franklin Gothic Medium"),
        plot.title = element_text(family = "Franklin Gothic Heavy"),
        legend.position = "none",
        plot.background = element_rect(fill = "whitesmoke"),
        panel.background = element_rect(fill = "whitesmoke"),
        panel.grid = element_line(color = "grey90")) +
  scale_fill_brewer(palette = "Dark2")+
  theme_minimal()
plt1_strip
```

```{r}
### Strip Chart of continent vs coastal proportion
plt1_strip <- ggplot(waste_2010, aes(x = reorder(continent_name, coastal_prop, FUN = median),y = coastal_prop)) +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#999999")) +
  geom_jitter(position=position_jitter(0.2), cex=1.2) +
  stat_summary(fun.y=mean, geom="point", shape=18,
                 size=3, color="red")+
   labs(title = "continent vs coastal proportion",
       caption = "",
       x = "Continent", y = "Coastal Proportion") +
  theme(text = element_text(family = "Franklin Gothic Medium"),
        plot.title = element_text(family = "Franklin Gothic Heavy"),
        legend.position = "none",
        plot.background = element_rect(fill = "whitesmoke"),
        panel.background = element_rect(fill = "whitesmoke"),
        panel.grid = element_line(color = "grey90")) +
  scale_fill_brewer(palette = "Dark2")+
  theme_minimal()
plt1_strip
```

```{r}
### Strip Chart of continent vs coastal proportion
# Strip Chart with Violin
plt1_strip_violin <- ggplot(waste_2010, aes(x = reorder(continent_name, coastal_prop, FUN = median),y = coastal_prop)) +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#999999")) +
  geom_violin(trim = FALSE)+
  geom_jitter(position=position_jitter(0.2), cex=1.2) +
  stat_summary(fun.y=mean, geom="point", shape=18,
                 size=3, color="red")+
 labs(title = "continent vs coastal proportion",
       caption = "",
       x = "Continent", y = "Coastal Proportion") +
  theme(text = element_text(family = "Franklin Gothic Medium"),
        plot.title = element_text(family = "Franklin Gothic Heavy"),
        legend.position = "none",
        plot.background = element_rect(fill = "whitesmoke"),
        panel.background = element_rect(fill = "whitesmoke"),
        panel.grid = element_line(color = "grey90")) +
  scale_fill_brewer(palette = "Dark2")+
  theme_minimal()
plt1_strip_violin
```
